---
title: "tutorial"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{tutorial}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(OLS)
```

The main part in this package is to train a linear regression model using 
ordinary least square method by function OLS. Inputting data, target response 
and predictor of interest, OLS fits linear model and provides results in a list including estimates, residuals and its degree of freedom. Value variance gives 
R squared statistics to evaluate the fitting result. Value summary gives a integrated output of fitted model, including estimates and hypothesis tests.

```{r}
outcome1 = "mpg"
predictors1 = c("cyl", "hp", "wt")
m1 = OLS(mtcars, outcome1, predictors1, through_origin=FALSE)
m1$coefficients
m1$residuals
m1$df.residuals
m1$variance
m1$summary
```

OLS can also fit linear model through the origin.

```{r}
m2 = OLS(mtcars, outcome1, predictors1, through_origin=TRUE)
m2$summary
```

Compare OLS function with build-in function lm() in terms of accuracy and time cost. As we can see from below, output of two functions are exactly the same. The speed of OLS function is slightly slower than lm().

```{r}
m3 = lm(mpg~cyl+hp+wt, data=mtcars)
m1$summary
m1$variance
summary(m3)
```

```{r}
t1 = m1$coefficients
t1 = round(t1, digits=3)
t2 = m3$coefficients
t2 = round(t2, digits=3)
names(t1) = NULL
names(t2) = NULL
bench::mark(t1, t2)
```

There are other function in the package to abundant the analysis. CI gives confidence interval of estimates in the model. Proper confidence level and variables can be selected. 

```{r}
CI(m1, c("cyl", "hp"), level=0.9)
```

Compare CI function with build-in function confint() in terms of accuracy and 
time cost. As we can see from below, output of two functions are exactly the 
same. The speed of CI function is slightly slower than confint().

```{r}
CI(m1, c("cyl", "hp"), level=0.9)
confint(m3)
```

```{r}
t3 = CI(m1, c("cyl", "hp"), level=0.95)[,c("2.5 %", "97.5 %")]
t4 = confint(m3, parm=c("cyl", "hp"))
t3 = round(t3, digits=3)
t4 = round(t4, digits=3)
bench::mark(t3, t4)
```

AOV function gives a detailed analysis of variance table for linear model.

```{r}
AOV(m1)
```

Compare AOV function with build-in function anova() in terms of accuracy and 
time cost. As we can see from below, output of two functions are exactly the 
same. The speed of AOV function is slightly slower than anova().

```{r}
AOV(m1)
anova(m3)
```

```{r}
t5 = AOV(m1)[c("cyl", "hp", "wt", "Residuals"), "Sum of Squares"]
t6 = anova(m3)[,"Sum Sq"]
t5 = round(t5, digits=1)
t6 = round(t6, digits=1)
names(t5) = NULL
names(t6) = NULL
bench::mark(t5, t6)
```
