---
title: "tutorial"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{tutorial}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(OLS)
```

The main part in this package is to train a linear regression model using 
ordinary least square method by function OLS. Inputting data, target response 
and predictor of interest, OLS fits linear model and provides results in a list including estimates, residuals and its degree of freedom. Value variance gives 
R squared statistics to evaluate the fitting result. Value summary gives a integrated output of fitted model, including estimates and hypothesis tests.

```{r}
outcome1 = "mpg"
predictors1 = c("cyl", "hp", "wt")
m1 = OLS(mtcars, outcome1, predictors1, through_origin=FALSE)
m1$coefficients
m1$residuals
m1$df.residuals
m1$variance
m1$summary
```

OLS can also fit linear model through the origin.

```{r}
m2 = OLS(mtcars, outcome1, predictors1, through_origin=TRUE)
m2$summary
```

Compare OLS function with build-in function lm() in terms of accuracy and time cost. As we can see from below, output of two functions are exactly the same.

```{r}
m3 = lm(mpg~cyl+hp+wt, data=mtcars)
m1$summary
m1$variance
summary(m3)
```

There are other function in the package to abundant the analysis. CI gives confidence interval of estimates in the model. Proper confidence level and variables can be selected.

```{r}
CI(m1, c("cyl", "hp"), level=0.9)
```

Compare CI function with build-in function confint() in terms of accuracy and 
time cost. As we can see from below, output of two functions are exactly the 
same.

```{r}
CI(m1, c("cyl", "hp"), level=0.9)
confint(m3)
```

AOV function gives a detailed analysis of variance table for linear model.

```{r}
AOV(m1)
```

Compare AOV function with build-in function anova() in terms of accuracy and 
time cost. As we can see from below, output of two functions are exactly the 
same.

```{r}
AOV(m1)
anova(m3)
```

